An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-25 paper/paper.tex
Paper: proofreading

% highlights of methodology
In order to determine whether or not our system provides solutions for the challenges of both P2P and centralized backup systems, we created test scenarios that test how well our system handles these challenges. We first tested how BitTorrent Sync handles a varying number of files to backup by backing 1G of data split up into 1 1GB file, 10 100MB files, and 100 10MB files and measuring the rates of data transfer over time. This was done on a network with just enough peers to have one file backed up with sufficient replication.

The second test scenario that we performed tested our system in a more realistic environment. Each instance of this scenario involved creating 100 peers on a network using MTA SZTAKI's cloud computing environment: SZTAKI Cloud. This scenario measured the effects of node churn, or the rate at which nodes go on and offline, on our system. Specifically, we measure how much network traffic is generated due to churn, since node unavailability is handled by moving replicas to different nodes. We take this measurement by running a test instance with no churn, and then running another where nodes periodically start and stop our BTBackup program. To make the test environment more realistic, we had each peer limit their download and upload speeds to values that are based off of worldwide Internet bandwidth statistics.

>>>>

% highlights of methodology
In order to determine whether or not our system provides solutions for the challenges of both P2P and centralized backup systems, we created test scenarios that test how well our system handles these challenges. We first tested how BitTorrent Sync handles a varying number of files to backup by backing up 1 GB of data split up into one 1GB file, ten 100MB files, and one hundred 10MB files, and measuring the rates of data transfer over time. This was done on a network with just enough peers to have one file backed up with sufficient replication.

The second test scenario that we performed tested our system in a more realistic environment. Each instance of this scenario involved creating 100 peers on a network using MTA SZTAKI's cloud computing environment: SZTAKI Cloud. This scenario measured the effects of node churn, or the rate at which nodes go on and offline, on our system. Specifically, we measure how much network traffic is generated due to churn, since node unavailability is handled by moving replicas to different nodes. We take this measurement by running a test instance with no churn, and then running another one with churn. To make the test environment more realistic, we had each peer limit their download and upload speeds to values that are based off of worldwide Internet bandwidth statistics.
